rang: Reconstructing reproducible R computational environments with ease

### 2023-02-17 paper/paper.rmd
Add political analysis and readme

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating instructions for other researchers to completely reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commericial service. The description generated by rang satisfies the definition of a reproducibile compendium and can be shared as such.
keywords:
  - R
  - reproducibility
  - docker
date: 02 February 2023
year: 2023
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

@@

```sh
rfiles=(0_data_aggregation.R 1_data_cleaning.R 2_analysis.R 3_plotting.R)
for i in ${rfiles[@]}
do
	Rscript $i
	code=$?
	if [ $code != 0 ]
	then
		exit 1
	fi
done   
```

@@

>>>>

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating instructions for other researchers to completely reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commericial service. The description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such.
keywords:
  - R
  - reproducibility
  - docker
date: 02 February 2023
year: 2023
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

@@

```sh
cd materials
rfiles=(0_data_aggregation.R 1_data_cleaning.R 2_analysis.R 3_plotting.R)
for i in ${rfiles[@]}
do
	Rscript $i
	code=$?
	if [ $code != 0 ]
	then
		exit 1
	fi
done   
```

@@

## Political Analysis

The study by @trisovic:2022 evaluates the reproducibility of R scripts shared on Dataverse. They found that 75\% of R scripts cannot be successfully executed. Among these failed R scripts is an R script shared by @beck:2019:EGD.

This R script has been "rescued" by the author of the R package `groundhog` [@groundhogrpkg], as demonstrated in a blog post [^groundhog]. We were wondering if `rang` can also be used to rescue the concerned R script.

The date of the R script, as indicated on Dataverse, is 2018-12-12. This date is used as the snapshot date.

```r
graph <- resolve(c("foreign", "bife"), snapshot_date = "2018-12-12")
dockerize(graph, output_dir = "nat", materials_dir = "nathaniel")
```

```r
cd nat
docker build -t nat .
docker run --rm --name "natcontainer" --entrypoint bash -ti nat
```

Inside the container

```r
cd materials
Rscript fn_5.R
```

The same file can also be "rescued" by `rang`.

[^groundhog]: http://datacolada.org/100

## Resuscitate a discontinued reproducible format

cacher
